Chapter X : Review of Methods for Solving the AX\raisebox{.2ex}{=}XB Sensor Calibration Problem

### 2015-08-26 AXXB_Review/AXXB Review.tex
To be continued

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{\textcolor{blue}{Note}}{\textcolor{blue}{For SE(3) and se(3) maybe make the inline matrices into actual matrices, it looks a little strange to me the way they are currently. Also, possibly consider changing $\Xi$ to $\mathfrak{h}$. Also, can you align the beginning of all of the second entries?}}
\entry{$SO(3)$}{$SO(3) \doteq \{R \, | \, RR^{T} = R^{T}R = \mathbb{I}$\textbf{\textcolor{blue}{,}} %and
 $\det(R) = 1$\textbf{\textcolor{blue}{,}} where $R \in \mathbb{R}^{3 \times 3}\}$}
\entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \time 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
\entry{$so(3)$}{$so(3) \doteq \{\Omega \,| \, R = exp(\Omega)$, where $\Omega \in \mathbb{R}^{3 \times 3}$ and $R \in SO(3)$ $\}$}
\entry{$se(3)$}{$se(3) \doteq \{\Xi \, | \, H = exp(\Xi)$, where $\Xi =\left(\Omega \; \xi; \; {\bf 0}^{T} 0 \right)$ and $\Omega \in \textcolor{blue}{so}%SO
(3), \, \xi \in \mathbb{R}^{3}, \, H \in SE(3) \}$}
\entry{$exp()$}{The matrix exponential of a square matrix. }
\entry{$log()$}{The matrix logarithm of a square matrix}
\entry{$H$}{A general rigid body transformation ($H \in SE(3)$) }
\entry{$\mathfrak{H}$}{ If $H$ is an element of a Lie Group, $\mathfrak{H}$ is the corresponding element in the Lie algebra}
\entry{$\mathbb{O}_n$}{$n \times n$ zero matrix}
\entry{$\mathbb{I}_n$}{$n \times n$ identity matrix}
\entry{$\{E_i\}$}{the set of ``natural" basis elements for Lie algebra}
\entry{$^\vee$}{For Lie algebra, the ``vee" operator is defined such that $\left(\displaystyle\sum\limits_{i=1}^n x_iE_i\right)^{\vee}\doteq(x_1,x_2,...,x_n)^T$ where $n = 3$ for $so(3)$ and $n = 6$ for $se(3)$}
\entry{$\hat{}$}{For Lie algebra, the ``hat" operator is the inverse of the ``vee" operator. $\widehat{(x_1,x_2,...,x_n)^T} \doteq \left( \displaystyle\sum\limits_{i=1}^n x_iE_i \right)$}
\entry{$\circ$}{The operator defined for the group product}
\entry{$\odot$}{The operator defined for the quaternion product}
\entry{$\hat{\odot}$}{The operator defined for the dual quaternion product}
\entry{$\otimes$}{The operator defined for the Kronecker product}
\entry{$vec$}{The ``vec'' operator is defined such that $vec(A) = [a_{11},...,a_{1m},a_{21},...,a_{2m},...,a_{n1},...,a_{nm}]^{T}$ for $A = [a_{ij}] \in \mathbb{R}^{m \times n}$}
\entry{\textcolor{blue}{Remark:}}{\textcolor{blue}{I would remove the next entry, it will lead to confusion and generally isn't necessary.}}
\entry{${\bf p}$}{For $P\in G$ (where $G$ is a Lie group, e.g. $SE(3)$ or $SO(3)$), ${\bf p}=(p_1,p_2,...,p_n)^T=\log^{\vee}(P)$}
\entry{$A_i$}{A rigid body transformation ($A_i \in SE(3)$), associated with one sensor measurement source}
\entry{$B_i$}{A rigid body transformation ($B_i \in SE(3)$), usually associated with a different sensor measurement source}
\entry{$X$}{The rigid body transformation ($\textcolor{blue}{X} %X_i 
\in SE(3)$) that relates $A_i$ to $B_i$}
\entry{$R_{H}$}{The rotation matrix of any general transformation matrix $H \in SE(3)$}
\entry{$\ttt_{H}$}{The translation vector of any general transformation matrix $H \in SE(3)$}
\entry{$\nn_{H}$}{The axis of rotation for $R_{H}$}
\entry{$\tilde{\nn}$}{The skew-symmetric representation of the axis of rotation ($\nn_{H}$) \textcolor{blue}{If you use $\Omega$ earlier you should try to keep some continuity}}
\entry{$\theta_{H}$}{The angle of rotation for $R_{H}$ about $\nn_{H}$}
\entry{$\rho$}{A probability distribution of $H\in G$ on SE(3)\textcolor{blue}{G not well-defined here}}
\entry{$M$}{For $\rho$, $M$ is the mean of the distribution}
\entry{$\Sigma$}{For $\rho$, $\Sigma$ is the covariance of the distribution about the mean, $M$}
\entry{$Ad$}{For the Lie group $G$ and the Lie algebra $\mathfrak{G}$, the adjoint operator is the transformation\\ Ad: $G \rightarrow$ GL($\mathfrak{G}$), defined as\\ Ad($H_1$)$\mathfrak{H}_2 \doteq \frac{d}{dt}(H_1 \circ e^{t \mathfrak{H}_2} \circ H_1^{-1})$}
\entry{$Ad(H) $}{The adjoint matrix with columns $(H E_i H^{-1})^{\vee}$}
\end{nomenclature}

@@

In the fields of robotics and computer vision, sensor calibration problems are often codified using the ``AX=XB'' formulation, (\textcolor{blue}{Figs.~\ref{AXXBfig1}--\ref{AXXBfig3}}%Fig.\ref{AXXBfig1}, Fig.\ref{AXXBfig2}, Fig.\ref{AXXBfig3}
). Example applications include camera calibration, Cartesian robot hand calibration, robot eye-to-hand calibration \cite{tsai1989new}, aerial vehicle sensor calibration \cite{darius1}, image-guided therapy (IGT) sensor calibration and endoscopic surgery \cite{schmidt2003robust}. An alternative name that describes this system is ``hand-eye'' calibration. Several methods \textcolor{blue}{exist} %have existed 
in the literature that can perform hand-eye calibration without directly dealing with the $AX=XB$ formulation such as \cite{malm2000new,heller2012branch,ruland2012globally,wu2014hand,kim,liu2015calibration}. %Camera calibration is also integrated into hand-eye calibration  in some works \cite{,,,}. 
Another problem, called the robot-world and hand-eye calibration, deals with the case where an additional calibration of the robot pose with respect to the world \textcolor{blue}{frame} is needed. This calibration technique is formulated as the ``AX=YB'' problem and multiple methods have been \textcolor{blue}{developed} %brought up 
such as \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative,li2010simultaneous,ernst2012non,heller2014hand}.
Furthermore, a hand-eye, tool-flange, and robot-robot calibration problem is formulated as the ``AXB = YCZ'' problem in \cite{wang2014towards}.

In the ``AX=XB'' formulation $A$, $X$, and $B$ are each homogeneous transformations (i.e., elements of the special Euclidean group, $SE(3)$) with each pair of measurements $(A,B)$ coming from sensors such as cameras, ultrasound probes, optical, or electromagnetic pose tracking systems, among others. $X$ is the unknown rigid-body \textcolor{blue}{transformation} %motion 
that is found as a result of solving $AX=XB$. It is well known that it is not possible to solve for
a unique $X$ from a single pair of exact $(A,B)$, but if there are two instances of independent exact measurements, $(A_1,B_1)$ and $(A_2,B_2)$ satisfying certain constraints,
then the problem can be solved \textcolor{blue}{for a unique, fixed $X$}. However, in practice, sensor noise is always present, and an exact solution is not possible. The goal, therefore, becomes one of finding
an $X$ with the least error given corresponding noisy pairs \textcolor{blue}{of data} $(A_i, B_i)$ for i = 1,2, \ldots,n.

@@

Given:
\begin{equation}
A X = X B
\label{mainaxxb}
\end{equation}
where $A,  B, X \in SE(3)$, it is well known that, in non-degenerate cases, there are two unspecified degrees of freedom to the problem for a single pair of sensor measurements, $(A,B)$. This situation is rectified by considering two pairs of exact measurements of the form in Eq.~(\ref{mainaxxb}), i.e., $ {A_1}X=X{B_1} {\rm \,\, and \,\,} {A_2}X = X{B_2} $, provided that some mild conditions are observed for the selection of the pairs $(A_1,B_1)$ and $(A_2,B_2)$ \cite{chen91,park1994robot,shiu1989calibration}. Note that $(A_i, B_i)$ here are relative transformation data pairs, so in real experiments at least 3 absolute transformation data pairs \textcolor{blue}{have to} %should 
be measured. Additionally, if there is sensor measurement error, then it may not be possible to find compatible pairs that reproduce the exact value of $X$. For this reason, minimization and least squares approaches are often taken over large sets of $A$s and $B$s.

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/UR5_Frame_Final.jpg}
\caption{\textcolor{blue}{Capitalization style changed midway through, I would use all lower case besides beginning of sentences} Application of AX=XB in Ultrasound Sensor Calibration: An Ultrasound Probe Is Attached to the End-effector and the Calibration Phantom Is Used for Ultrasound Probe Calibration. (The UR5 robot pictured above is owned by Professor Emad Boctor of Johns Hopkins University)}
\label{AXXBfig2}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/Robot_Patern.jpg}
\caption{\textcolor{blue}{Labels are hard to see in the picture. Also, you change the capitalization style midway through} Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
 \textit{Boston Dynamics} Requires Head-Body Calibration before Turning the Knob. Different pairs of $(A_i, B_i)$ are measured by changing the head pose of the humanoid robot. (This picture was generated using the open-source robot simulation software Gazebo)}
\label{AXXBfig3}
\end{figure}

@@

%A wide variety of such metrics are discussed in \cite{axxb13} that have the useful property of left-invariance, $d(H_0 H_1, H_0 H_2) = d(H_1, H_2)$ for any $H_0, H_1, H_2 \in SE(3)$.
%
%
%Perhaps the simplest of the left-invariant ones is based on the weighted Frobenius norm
%$$ d^2(H_1,H_2) = \|H_1 - H_2\|_{W}^{2} = {\rm trace}[(H_1 - H_2)W(H_1 - H_2)^T] $$
%where $W$ is a matrix that weights rotations and translations appropriately, as described in \cite{axxb13}.
%The sets of pairs $(A_i,B_i)$ for $i=1,2...,n$ is chosen such
%that the set $\{A_i\}$ is spread out over a variety of positions and orientations, and likewise for $\{B_i\}$, so that the
%resulting $X$ is robust to measurement errors. 
This chapter is organized as follows. 
In Section~\ref{sec:sol_methods}, a detailed review is given for the existing methods that solve the $AX=XB$ problem using pairs of $\{A_{i}, B_{i}\}$ with correspondence. The notation used throughout the literature is not consistent and the authors \textcolor{blue}{strove} %tried their best 
to standardize the notation used across the reviewed methods
\textcolor{blue}{to provide the readers with a straightforward and consistent representation of the methods and their relationships.} %so that readers can have a straightforward and consistent understanding of the methods and their relationships. 
Some approaches are preferable under certain circumstances and their advantages and disadvantages are also highlighted. 
In Section~\ref{sec:data_selection}, some important criterion for data selection and different errors metrics used in the literature are presented. 
%In section 5, numerical simulations are performed on the selected methods and further conclusions are given based on the results of the simulation. 
Finally, in Section~\ref{sec:conclusion} a complete summary of the $AX=XB$ solvers is provided and open problems are noted as well.

@@

The closed form expression for $R_{X}$ is:
\textcolor{blue}{Note: It is hard to \~n in the below equation and also the 2nd subscript on R$_X$}
\begin{equation}
R_{X} = e^{\tilde{\nn}_{A}\beta}R_{X_{P}}
\label{RotationCheng}
\end{equation}
where 
\begin{center}
$R_{X_{p}} =  e^{\tilde{\nn}_{X}\theta_{X}}$\\
$\nn_{X} = \nn_{B} \times \nn_{A}$\\
$\theta_{X} = \rm atan2(|\nn_{B} \times \nn_{A}|,\nn_{B} \cdot \nn_{A})$\\
\end{center}
and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\tilde{\nn}$ is a skew-symmetric matrix defined as below:\\
\begin{equation}
\tilde{\nn}
=
\begin{pmatrix}
0 & -n_{3} & n_{2} \\
n_{3} & 0 & -n_{1} \\
-n_{2} & n_{1} & 0
\end{pmatrix}.
\end{equation}

@@

\subsection{Dual Quaternion Method }
The dual quaternion method proposed by Daniilidis and Bayro-Corrochano \cite{daniilidis1996dual} (Daniilidis \cite{daniilidis1999hand}) treats the rotation and translation parts of the matrix X in a unified way and facilitates a new simultaneous solution of X using SVD. To begin, Eq.~(\ref{mainaxxb}) is transformed into an equation \textcolor{blue}{of dual quaternions:} %in dual quaternion form as follows:
\begin{equation}
AX = XB 
\; \;
\Leftrightarrow
\; \;
\check{a} = \check{q}_{X}\hat{\odot}\check{b}\hat{\odot}\bar{\check{q}}_{X}
\label{DualQuaternion}
\end{equation}
where $\check{a}$, $\check{b}$ and $\check{q}$ are the dual quaternions that represent matrices $A$, $B$ and $X$, and $\bar{\check{q}}$ is the conjugate of $\check{q}$.

The dual quaternion that corresponds to a \textcolor{blue}{Be consistent throughout the paper: 4x4} %4 by 4 
rigid transformation matrix is defined as follows:
\begin{equation}
\check{q}_{X} =
\Bigg( 
\begin{array}{c}
\cos(\frac{\theta + \epsilon d}{2})\\
\sin(\frac{\theta + \epsilon d}{2})({\bf l} + \epsilon {\bf m})
\end{array}
\Bigg)
\label{dual_screw}
\end{equation}
where
$\theta$, $d$, ${\bf l}$ and ${\bf m}$ are screw parameters and ${\epsilon}^{2} = 0$. $\theta$ is the rotation angle, $d$ is the pitch, $\vec{\bf l}$ is the direction of the screw, and ${\bf m} = {\bf p} \times {\bf l}$ is the line moment where ${\bf p}$ is a point on the line. The six tuple $({\bf l}, {\bf m})$ defines a line in 3-D space. Furthermore, by expanding the dual terms in $\check{q}_{X}$, Eq.~(\ref{dual_screw}) can also be written as:
\begin{equation}
\check{q}_{X} = q_{X} + \epsilon {q}^{\prime}_{X}.
\end{equation} 
Both $q$ and $q^{\prime}$ are quaternions satisfying the following constraints:
\begin{equation}
{\bf q}^{T}_{X}{\bf q}_{X} = 1 \; \; \text{and} \;
\; {\bf q}^{T}_{X}{\bf q}^{\prime}_{X} = 0.
\end{equation}
Similar to Section \textcolor{blue}{\ref{sec:quats}?}, ${\bf q}_{X}$ and ${\bf q}^{\prime}_{X}$ are the vector representations of $q_{X}$ and $q^{\prime}_{X}$.
Then equation $A_{i}X = XB_{i}$ can be converted into the form below:

@@

\subsection{Optimization Methods}
\label{sec:optimization}
Different optimization methods have been proposed in the literature and most of them are built upon the various parametrizations of the $AX=XB$ equations mentioned previously. 
\subsubsection{Quaternion Based Simultaneous Approach}
When trying to solve for $R_{X}$ and $\ttt_{X}$ simultaneously, it is impossible to find a closed-form solution. Horaud and Dornaika \cite{horaud1995hand} presented an objective function for minimization, which is a sum of squares of nonlinear functions as:
\begin{equation}
\begin{split}
f(q_X,\ttt_{X}) = \lambda_{1} \sum_{i = 1}^{n}||vec(q_{X} \odot t_{B_{i}} \odot \bar{q}_{X}) -(R_{A_i} - \mathbb{I})\ttt_{X} - \ttt_{A_i}||^{2}\\
\lambda_{2} \sum_{i = 1}^{n}||{n_{A_{i}} - q_{X} \odot n_{B_{i}} \odot \bar{q}_{X}}||^{2} + \lambda_{3}(1 - \qq_{X}^{T}\qq_{X})^2\\
\textcolor{blue}{I believe you are missing an operator between the two lines} 
\end{split}
\label{simlqua}
\end{equation}
where $\lambda_1, \lambda_2, \lambda_3 \in \mathbb{R}$. Note that $vec()$ here represents the vector part of a quaternion such that $vec(q) \in \mathbb{R}^{3}$. The third term is a penalty function where the \textcolor{blue}{modulus,modulo?} %module 
of $q$ will approach 1 when $\lambda_{3}$ becomes large. This is a non-convex optimization problem which requires a good initial guess due to the existence of multiple local minima. However, the result can be more accurate than the rest of the solvers for certain motion pairs when the initial guess is ``good".

@@

When the $AX=XB$ problem is formulated as a dual quaternion representation as in Eq.~(\ref{dqua}), the equivalent $L_\infty$ optimization problem can be written as:
\begin{equation}
\begin{split}
&\underset{\delta, \xx}{\text{min}} \; \; \delta \\
&\text{subject to} \; \; ||S_i\xx||_2 \leq \delta \\
&\text{where} \; \; i = 1,2,...,n \; \; \text{with} \; \; \bf{Dx \geq f}.
\end{split}
\end{equation}
The matrix $S_i$ and vector $\bf x$ correspond to those in Eq.~(\ref{dqua}). 
The inequality constraint $\bf{Dx \geq f}$ is added manually in order to prevent $\xx$ from reaching zero, which is a meaningless solution for the program. \textcolor{blue}{$\bf x$ must also satisfy two additional constraints: $\|\qq_X\|=1$ and $\|\qq_{X}^{\prime}\|=1$.}%Another constraint $\bf x$ has to satisfy is that $||\qq_X||=1$ and $||\qq_{X}^{\prime}||=1$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{\textcolor{blue}{Note}}{\textcolor{blue}{For SE(3) and se(3) maybe make the inline matrices into actual matrices, it looks a little strange to me the way they are currently. Also, possibly consider changing $\Xi$ to $\mathfrak{h}$. Also, can you align the beginning of all of the second entries?}}
\entry{$SO(3)$}{$SO(3) \doteq \{R \, | \, RR^{T} = R^{T}R = \mathbb{I}$\textbf{\textcolor{blue}{,}} %and
 $\det(R) = 1$\textbf{\textcolor{blue}{,}} where $R \in \mathbb{R}^{3 \times 3}\}$}
\entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \times 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
\entry{$so(3)$}{$so(3) \doteq \{\Omega \,| \, R = exp(\Omega)$, where $\Omega \in \mathbb{R}^{3 \times 3}$ and $R \in SO(3)$ $\}$}
\entry{$se(3)$}{$se(3) \doteq \{\Xi \, | \, H = exp(\Xi)$, where $\Xi =\left(\Omega \; \xi; \; {\bf 0}^{T} 0 \right)$ and $\Omega \in \textcolor{blue}{so}%SO
(3), \, \xi \in \mathbb{R}^{3}, \, H \in SE(3) \}$}
\entry{$\exp()$}{The matrix exponential of a square matrix. }
\entry{$\log()$}{The matrix logarithm of a square matrix}
\entry{$H$}{A general rigid body transformation ($H \in SE(3)$) }
\entry{$\mathfrak{H}$}{ If $H$ is an element of a Lie Group, $\mathfrak{H}$ is the corresponding element in the Lie algebra}
\entry{$\mathbb{O}_n$}{$n \times n$ zero matrix}
\entry{$\mathbb{I}_n$}{$n \times n$ identity matrix}
\entry{$\{E_i\}$}{the set of ``natural" basis elements for Lie algebra}
\entry{$^\vee$}{For Lie algebra, the ``vee" operator is defined such that $\left(\displaystyle\sum\limits_{i=1}^n x_iE_i\right)^{\vee}\doteq(x_1,x_2,...,x_n)^T$ where $n = 3$ for $so(3)$ and $n = 6$ for $se(3)$}
\entry{$\widehat{}$}{For Lie algebra, the ``hat" operator is the inverse of the ``vee" operator. $\widehat{(x_1,x_2,...,x_n)^T} \doteq \left( \displaystyle\sum\limits_{i=1}^n x_iE_i \right)$; For a vector ${\bf n} \in \mathbb{R}^{3 \times 1}$. $\widehat{\bf n}$ represents the corresponding skew symmetric matrix }
\entry{$\circ$}{The operator defined for the group product}
\entry{$\odot$}{The operator defined for the quaternion product}
\entry{$\hat{\odot}$}{The operator defined for the dual quaternion product}
\entry{$\otimes$}{The operator defined for the Kronecker product}
\entry{$vec$}{The ``vec'' operator is defined such that $vec(A) = [a_{11},...,a_{1m},a_{21},...,a_{2m},...,a_{n1},...,a_{nm}]^{T}$ for $A = [a_{ij}] \in \mathbb{R}^{m \times n}$}
\entry{$A_i$}{A rigid body transformation ($A_i \in SE(3)$), associated with one sensor measurement source}
\entry{$B_i$}{A rigid body transformation ($B_i \in SE(3)$), usually associated with a different sensor measurement source}
\entry{$X$}{The rigid body transformation ($X %X_i 
\in SE(3)$) that relates $A_i$ to $B_i$}
\entry{$R_{H}$}{The rotation matrix of any general transformation matrix $H \in SE(3)$}
\entry{$\ttt_{H}$}{The translation vector of any general transformation matrix $H \in SE(3)$}
\entry{$\nn_{H}$}{The axis of rotation for $R_{H}$}
\entry{$\widetilde{\nn}$}{The skew-symmetric representation of the axis of rotation ($\nn_{H}$) \textcolor{blue}{If you use $\Omega$ earlier you should try to keep some continuity}}
\entry{$\theta_{H}$}{The angle of rotation for $R_{H}$ about $\nn_{H}$}
\entry{$\rho$}{A probability distribution of $H\in G$, where G $\subset$ SE(3)}
\entry{$M$}{For $\rho$, $M$ is the mean of the distribution}
\entry{$\Sigma$}{For $\rho$, $\Sigma$ is the covariance of the distribution about the mean, $M$}
\entry{$Ad$}{For the Lie group $G$ and the Lie algebra $\mathfrak{G}$, the adjoint operator is the transformation\\ Ad: $G \rightarrow$ GL($\mathfrak{G}$), defined as\\ Ad($H_1$)$\mathfrak{H}_2 \doteq \frac{d}{dt}(H_1 \circ e^{t \mathfrak{H}_2} \circ H_1^{-1})$}
\entry{$Ad(H) $}{The adjoint matrix with columns $(H E_i H^{-1})^{\vee}$}
\end{nomenclature}

@@

In the fields of robotics and computer vision, sensor calibration problems are often codified using the ``AX=XB'' formulation, (Figs.~\ref{AXXBfig1}--\ref{AXXBfig3}%Fig.\ref{AXXBfig1}, Fig.\ref{AXXBfig2}, Fig.\ref{AXXBfig3}
). Example applications include camera calibration, Cartesian robot hand calibration, robot eye-to-hand calibration \cite{tsai1989new}, aerial vehicle sensor calibration \cite{darius1}, image-guided therapy (IGT) sensor calibration and endoscopic surgery \cite{schmidt2003robust}. An alternative name that describes this system is ``hand-eye'' calibration. Several methods exist %have existed 
in the literature that can perform hand-eye calibration without directly dealing with the $AX=XB$ formulation such as \cite{malm2000new,heller2012branch,ruland2012globally,wu2014hand,kim,liu2015calibration}. %Camera calibration is also integrated into hand-eye calibration  in some works \cite{,,,}. 
Another problem, called the robot-world and hand-eye calibration, deals with the case where an additional calibration of the robot pose with respect to the world frame is needed. This calibration technique is formulated as the ``AX=YB'' problem and multiple methods have been developed %brought up 
such as \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative,li2010simultaneous,ernst2012non,heller2014hand}.
Furthermore, a hand-eye, tool-flange, and robot-robot calibration problem is formulated as the ``AXB = YCZ'' problem in \cite{wang2014towards}.

In the ``AX=XB'' formulation $A$, $X$, and $B$ are each homogeneous transformations (i.e., elements of the special Euclidean group, $SE(3)$) with each pair of measurements $(A,B)$ coming from sensors such as cameras, ultrasound probes, optical, or electromagnetic pose tracking systems, among others. $X$ is the unknown rigid-body transformation %motion 
that is found as a result of solving $AX=XB$. It is well known that it is not possible to solve for
a unique $X$ from a single pair of exact $(A,B)$, but if there are two instances of independent exact measurements, $(A_1,B_1)$ and $(A_2,B_2)$ satisfying certain constraints,
then the problem can be solved for a unique, fixed $X$. However, in practice, sensor noise is always present, and an exact solution is not possible. The goal, therefore, becomes one of finding
an $X$ with the least error given corresponding noisy pairs of data $(A_i, B_i)$ for i = 1,2, \ldots,n.

@@

Given:
\begin{equation}
A X = X B
\label{mainaxxb}
\end{equation}
where $A,  B, X \in SE(3)$, it is well known that, in non-degenerate cases, there are two unspecified degrees of freedom to the problem for a single pair of sensor measurements, $(A,B)$. This situation is rectified by considering two pairs of exact measurements of the form in Eq.~(\ref{mainaxxb}), i.e., $ {A_1}X=X{B_1} {\rm \,\, and \,\,} {A_2}X = X{B_2} $, provided that some mild conditions are observed for the selection of the pairs $(A_1,B_1)$ and $(A_2,B_2)$ \cite{chen91,park1994robot,shiu1989calibration}. Note that $(A_i, B_i)$ here are relative transformation data pairs, so in real experiments at least 3 absolute transformation data pairs have to 
be measured. Additionally, if there is sensor measurement error, then it may not be possible to find compatible pairs that reproduce the exact value of $X$. For this reason, minimization and least squares approaches are often taken over large sets of $A$s and $B$s.

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/UR5_Frame_Final.jpg}
\caption{Application of AX=XB in ultrasound sensor calibration: an ultrasound probe is attached to the end-effector and the calibration phantom is used for ultrasound probe calibration. (The UR5 robot pictured above is owned by Professor Emad Boctor of Johns Hopkins University)}
\label{AXXBfig2}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/Robot_Patern.jpg}
\caption{\textcolor{blue}{Labels are hard to see in the picture. Also, you change the capitalization style midway through} Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
 \textit{Boston Dynamics} Requires head-body calibration before turning the knob. Different pairs of $(A_i, B_i)$ are measured by changing the head pose of the humanoid robot. (This picture was generated using the open-source robot simulation software Gazebo)}
\label{AXXBfig3}
\end{figure}

@@

%A wide variety of such metrics are discussed in \cite{axxb13} that have the useful property of left-invariance, $d(H_0 H_1, H_0 H_2) = d(H_1, H_2)$ for any $H_0, H_1, H_2 \in SE(3)$.
%
%
%Perhaps the simplest of the left-invariant ones is based on the weighted Frobenius norm
%$$ d^2(H_1,H_2) = \|H_1 - H_2\|_{W}^{2} = {\rm trace}[(H_1 - H_2)W(H_1 - H_2)^T] $$
%where $W$ is a matrix that weights rotations and translations appropriately, as described in \cite{axxb13}.
%The sets of pairs $(A_i,B_i)$ for $i=1,2...,n$ is chosen such
%that the set $\{A_i\}$ is spread out over a variety of positions and orientations, and likewise for $\{B_i\}$, so that the
%resulting $X$ is robust to measurement errors. 
This chapter is organized as follows. 
In Section~\ref{sec:sol_methods}, a detailed review is given for the existing methods that solve the $AX=XB$ problem using pairs of $\{A_{i}, B_{i}\}$ with correspondence. The notation used throughout the literature is not consistent and the authors strove %tried their best 
to standardize the notation used across the reviewed methods
\textcolor{blue}{to provide the readers with a straightforward and consistent representation of the methods and their relationships.} %so that readers can have a straightforward and consistent understanding of the methods and their relationships. 
Some approaches are preferable under certain circumstances and their advantages and disadvantages are also highlighted. 
In Section~\ref{sec:data_selection}, some important criterion for data selection and different errors metrics used in the literature are presented. 
%In section 5, numerical simulations are performed on the selected methods and further conclusions are given based on the results of the simulation. 
Finally, in Section~\ref{sec:conclusion} a complete summary of the $AX=XB$ solvers is provided and open problems are noted as well.

@@

The closed form expression for $R_{X}$ is:
\textcolor{blue}{Note: It is hard to \~n in the below equation and also the 2nd subscript on R$_X$}
\begin{equation}
R_{X} = \exp{(\widetilde{\nn}_{A}\beta)}R_{X_{P}}
\label{RotationCheng}
\end{equation}
where 
\begin{center}
$R_{X_{p}} =  \exp{(\widetilde{\nn}_{X}\theta_{X})}$\\
$\nn_{X} = \nn_{B} \times \nn_{A}$\\
$\theta_{X} = \rm atan2(|\nn_{B} \times \nn_{A}|,\nn_{B} \cdot \nn_{A})$\\
\end{center}
and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\widetilde{\nn}$ is a skew-symmetric matrix defined as below:\\
\begin{equation}
\tilde{\nn}
=
\begin{pmatrix}
0 & -n_{3} & n_{2} \\
n_{3} & 0 & -n_{1} \\
-n_{2} & n_{1} & 0
\end{pmatrix}.
\end{equation}

@@

\subsection{Dual Quaternion Method }
The dual quaternion method proposed by Daniilidis and Bayro-Corrochano \cite{daniilidis1996dual} (Daniilidis \cite{daniilidis1999hand}) treats the rotation and translation parts of the matrix X in a unified way and facilitates a new simultaneous solution of X using SVD. To begin, Eq.~(\ref{mainaxxb}) is transformed into an equation of dual quaternions: %in dual quaternion form as follows:
\begin{equation}
AX = XB 
\; \;
\Leftrightarrow
\; \;
\check{a} = \check{q}_{X}\hat{\odot}\check{b}\hat{\odot}\bar{\check{q}}_{X}
\label{DualQuaternion}
\end{equation}
where $\check{a}$, $\check{b}$ and $\check{q}$ are the dual quaternions that represent matrices $A$, $B$ and $X$, and $\bar{\check{q}}$ is the conjugate of $\check{q}$.

The dual quaternion that corresponds to a 4x4 %4 by 4 
rigid transformation matrix is defined as follows:
\begin{equation}
\check{q}_{X} =
\Bigg( 
\begin{array}{c}
\cos(\frac{\theta + \epsilon d}{2})\\
\sin(\frac{\theta + \epsilon d}{2})({\bf l} + \epsilon {\bf m})
\end{array}
\Bigg)
\label{dual_screw}
\end{equation}
where
$\theta$, $d$, ${\bf l}$ and ${\bf m}$ are screw parameters and ${\epsilon}^{2} = 0$. $\theta$ is the rotation angle, $d$ is the pitch, $\vec{\bf l}$ is the direction of the screw, and ${\bf m} = {\bf p} \times {\bf l}$ is the line moment where ${\bf p}$ is a point on the line. The six tuple $({\bf l}, {\bf m})$ defines a line in 3-D space. Furthermore, by expanding the dual terms in $\check{q}_{X}$, Eq.~(\ref{dual_screw}) can also be written as:
\begin{equation}
\check{q}_{X} = q_{X} + \epsilon {q}^{\prime}_{X}.
\end{equation} 
Both $q$ and $q^{\prime}$ are quaternions satisfying the following constraints:
\begin{equation}
{\bf q}^{T}_{X}{\bf q}_{X} = 1 \; \; \text{and} \;
\; {\bf q}^{T}_{X}{\bf q}^{\prime}_{X} = 0
\end{equation}
where ${\bf q}_{X}$ and ${\bf q}^{\prime}_{X}$ are the vector representations of $q_{X}$ and $q^{\prime}_{X}$.
Then equation $A_{i}X = XB_{i}$ can be converted into the form below:

@@

\subsection{Optimization Methods}
\label{sec:optimization}
Different optimization methods have been proposed in the literature and most of them are built upon the various parametrizations of the $AX=XB$ equations mentioned previously. 
\subsubsection{Quaternion Based Simultaneous Approach}
When trying to solve for $R_{X}$ and $\ttt_{X}$ simultaneously, it is impossible to find a closed-form solution. Horaud and Dornaika \cite{horaud1995hand} presented an objective function for minimization, which is a sum of squares of nonlinear functions as:
\begin{equation}
\begin{split}
f(q_X,\ttt_{X}) = \lambda_{1} \sum_{i = 1}^{n}||vec(q_{X} \odot t_{B_{i}} \odot \bar{q}_{X}) -(R_{A_i} - \mathbb{I})\ttt_{X} - \ttt_{A_i}||^{2}\\
+ \lambda_{2} \sum_{i = 1}^{n}||{n_{A_{i}} - q_{X} \odot n_{B_{i}} \odot \bar{q}_{X}}||^{2} + \lambda_{3}(1 - \qq_{X}^{T}\qq_{X})^2
\end{split}
\label{simlqua}
\end{equation}
where $\lambda_1, \lambda_2, \lambda_3 \in \mathbb{R}$. Note that $vec()$ here represents the vector part of a quaternion such that $vec(q) \in \mathbb{R}^{3}$. The third term is a penalty function where the modulus %module 
of $q$ will approach 1 when $\lambda_{3}$ becomes large. This is a non-convex optimization problem which requires a good initial guess due to the existence of multiple local minima. However, the result can be more accurate than the rest of the solvers for certain motion pairs when the initial guess is ``good".

@@

When the $AX=XB$ problem is formulated as a dual quaternion representation as in Eq.~(\ref{dqua}), the equivalent $L_\infty$ optimization problem can be written as:
\begin{equation}
\begin{split}
&\underset{\delta, \xx}{\text{min}} \; \; \delta \\
&\text{subject to} \; \; ||S_i\xx||_2 \leq \delta \\
&\text{where} \; \; i = 1,2,...,n \; \; \text{with} \; \; \bf{Dx \geq f}.
\end{split}
\end{equation}
The matrix $S_i$ and vector $\bf x$ correspond to those in Eq.~(\ref{dqua}). 
The inequality constraint $\bf{Dx \geq f}$ is added manually in order to prevent $\xx$ from reaching zero, which is a meaningless solution for the program. $\bf x$ must also satisfy two additional constraints: $\|\qq_X\|=1$ and $\|\qq_{X}^{\prime}\|=1$. %Another constraint $\bf x$ has to satisfy is that $||\qq_X||=1$ and $||\qq_{X}^{\prime}||=1$.
